Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Explains how the function is adapted to compute the directions in the latent space

>>>>

In the previous function, we have inverted the roles of the covariance matrix
(i.e., the Gram matrix in the test space) and the "Gram matrix" of the latent
space, which is the inverse of the covariance matrix. Also, we have computed a
"scale matrix" that is formed by the square root elements of the diagonal of the
Gram matrix, inverted (i.e. matrix $\mathbf{D}$ in the manuscript). Note that,
contrary to what happens in the test space (where the "scale" matrix is the
inverse of the standard deviation matrix), this scale matrix in the latent space
is "meaningless" (in terms of interpretation). Finally, in the test pace, the
covariance matrix was used in the computation of the cosines, but here the Gram
matrix is not; this makes sense since, as we have seen before, transforming from
the test to the latent space implies multiplying by the inverse of the
covariance matrix.
